\documentclass[margin,line]{res}

\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[unicode=true,
            colorlinks=true,
            linkcolor=blue]{hyperref}
\usepackage{longtable}
\hypersetup{urlcolor=BlueViolet} % Does not apply color to href's
\hypersetup{colorlinks,urlcolor=BlueViolet} % href's are correct, but navigation


\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\begin{document}
\newcommand{\link}[1]{\texttt{#1}}
\providecommand{\tightlist}{%
      \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}


\name{Mike McCarty\vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
%=========INFO=========
\begin{tabular}{@{}p{2in}p{4in}}
{\it email:}  mm@mikemccarty.io   & {\it web:} \href{http://mikemccarty.io}{mikemccarty.io} \\
\end{tabular}


%========= RESEARCH =========
\section{\sc Summary}
Experienced engineering leader focused on building Data Science and Machine Learning tools. Background in scientific computing, software engineering, leadership, and mentoring.

%========= WORK EXPERIENCE ==========
\section{\sc Professional Experience}

%\vspace{-.3cm}
{\bf NVIDIA} \\
{\em Senior Engineering Manager, Analytics and Data Intelligence} \hfill {\bf Apr 2024 - Present}\\
Managing Cloud and HPC Deployment, Build Engineering and DevOps teams
Supporting Analytics and Data Intelligence (ADI) and Agents, Retrieval, and Knowledge (ARK) orgs

{\em Engineering Manager, RAPIDS} \hfill {\bf Feb 2022 - Apr 2024}\\
Cloud, HPC and Scientific Computing 
Distributed Computing with Dask and Legate
PyData Open-source Projects (Dask, Conda-Forge, NumPy, Pandas, and Scikit-learn)

{\em Senior Product Manager, Python Developer Products} \hfill {\bf Jun 2021 - Feb 2022}\\
Product manager for Python Developer tools: Legate, cuNumeric, and CUDA Python

%\vspace{-.3cm}
{\bf NumFOCUS} \\
{\em Advisory Board Member} \hfill {\bf Aug 2021 - Sep 2024}\\

%\vspace{-.3cm}
{\bf Prefect Inc} \\
{\em Advisory Board Member} \hfill {\bf Jan 2020 - Dec 2023}\\
Technical advisor on product offerings and open source development

%\vspace{-.3cm}
{\bf Capital One - Center for Machine Learning} \\
{\em Director of Software Engineering} \hfill {\bf July 2019 - May 2021}\\
{\em Senior Manager, Lead Software Engineer} \hfill {\bf Oct 2018 - July 2019}\\
Drove adoption of Dask and RAPIDS throughout the enterprise leading to
10-100x computational improvement for model training / predictions
and scaled train datasets 2 orders of magnitude.

Led organization building and maintaining custom machine learning tools for the enterprise.

Subject matter expert for the PyData and SciPy software stacks.

Contributed to open source projects (Dask, RAPIDS, XGBoost).

%\vspace{-.3cm}
{\bf Anaconda Inc} \\
{\em Platform Engineer and Open Source Developer} \hfill {\bf Oct 2017 - Oct 2018}\\
Platform engineer on enteprise products.
Open Source developer on data science and machine learning projects.

%\vspace{-.3cm}
{\bf Morehead State University - Dep. of Mathematics and Physics} - Morehead, KY\\
{\em Chairman of Advisory Board} \hfill {\bf 2016 - 2017}\\

%\vspace{-.3cm}
{\bf Zoomdata Inc} - Reston, VA\\
{\em Senior Software Engineer / Technical Lead} \hfill {\bf Sept 2016 - Oct 2017}\\
Developed and maintained Zoomdata, a Big Data Business Intelligence tool that is capable of connecting to modern data sources for visualization.
Led Application Platform development team, consisting of 6 engineers.

%\vspace{-.3cm}
{\bf Booz Allen Hamilton} - Washington, DC\\
{\em Lead Engineer} \hfill {\bf Mar 2016 - Sept 2017}\\
Led development of data management, ingest, analysis, and visualization on TCPI project for the Health and Human Services.

%\vspace{-.3cm}
{\bf Mission Data} - Washington, DC\\
{\em Principal Engineer} \hfill {\bf Feb 2015 - Mar 2016}\\

%\vspace{-.3cm}
{\bf Rivera Group, Inc} - Louisville, KY\\
{\em Software Architect / Product Development Manager} \hfill {\bf Nov 2013 - Feb 2015}\\

%\vspace{-.3cm}
{\bf Nub Games, Inc}\\
{\em Senior Software Engineer} \hfill {\bf Jan 2013 – Nov 2013}\\

%\vspace{-.3cm}
{\bf National Radio Astronomy Observatory} - Green Bank, WV\\
{\bf Software Engineer} \hfill {\bf Sept 2010 - Jan 2013}\\
Green Bank Telescope (GBT) Software Development Division

%\vspace{-.3cm}
{\bf National Institute for Computational Sciences / Oak Ridge National Lab} - Oak Ridge, TN\\
{\bf Systems Programmer} \hfill {\bf Aug 2009 - Aug 2010}\\
High Performance Computing Operations Group

%\vspace{-.3cm}
{\bf National Radio Astronomy Observatory} - Green Bank, WV\\
{\bf Software Engineer} \hfill {\bf Oct 2006 - Aug 2009}\\
Green Bank Telescope (GBT) Software Development Division

%\vspace{-.3cm}
{\bf National Radio Astronomy Observatory} - Charlottesville, VA\\
{\bf Software Engineer} \hfill {\bf May 2005 - Sept 2006}\\
Atacama Large Millimeter Array (ALMA) Front End Integration Center

%========= EDUCATION ==========
\section{\sc Education}

{\bf Stanford University}\\
%{\em Graduate School of Business}
\vspace*{-.1in}
\begin{list1}
\item[] Stanford LEAD Professional Certificate \hfill {\bf 2024}
\end{list1}

{\bf University of Illinois}, Urbana-Champaign, IL\\
%{\em Department of Computer Science}
\vspace*{-.1in}
\begin{list1}
\item[] Graduate Coursework \hfill {\bf 2011}
\end{list1}

{\bf Morehead State University}, Morehead, KY\\
%{\em Department of Mathematics and Physics}
\vspace*{-.1in}
\begin{list1}
\item[] B.S., Physics \hfill {\bf 2006}
\item[] B.S., Computer Science \hfill {\bf 2002}
\end{list1}

%=========== Skills ================
\section{\sc Skills}

\input{skills.tex}


%========= PUBLICATIONS ==========
\section{\sc Publications}

\input{publications.tex}


%=========== Footer ================
\end{resume}
\end{document}

